On multilevel constraint decomposition methods \\ for nonlinear variational inequalities

### 2021-07-07 paper/mcd2.tex
State the C_2 assumption.

@@

To prove the convergence of the basic algorithm we make two assumptions regarding the CD and the residual functional, as follows.

\begin{assumptions}  \emph{Lipschitz restrictions}: There exists a constant $C_1>0$ so that
\begin{equation}
\left(\sum_{i=0}^{m-1} \|R_i u - R_i v\|^2\right)^{1/2} \le C_1 \|u-v\| \label{as:lipschitzrestrictions}
\end{equation}
for all $u,v\in\cK$.  \emph{Totally Lipschitz residual}: There exists $C_2>0$ so that
\begin{equation}
FIXME \label{as:totallylipschitzresidual}
\end{equation}
for all FIXME
\end{assumptions}
Note that the constants $C_1,C_2$ generally depend on $m$.  % IF PROOF BELOW SUCCEEDS, SO ALGORITHM IS NORM DECREASING, THEN MAY BE ABLE TO ARGUE THAT IT IS O.K. FOR CONSTANTS TO DEPEND ON $u,v,w_{ij}$ etc. AS LONG AS THEY ARE UNIFORMLY BOUNDED ON CERTAIN BOUNDED SETS

Though the assumptions are technical in certain senses, the reader should note some essential features:
\begin{itemize}
\item The assumptions are identical to inequalities (7), (8) in \cite{Tai2003} where they are used them to prove the convergence of the optimization version of the basic CD algorithm.  See also their unconstrained versions, inequalities (13), (14) in \cite{TaiXu2002}.
\item Assumption \eqref{as:lipschitzrestrictions} addresses only the constraint decomposition while, essentially, \eqref{as:totallylipschitzresidual} addresses only a subspace decomposition property of the residual functional.  For example, if $f$ is defined by a PDE weak form, as in the classical obstacle problem, then \eqref{as:totallylipschitzresidual} is verified over the subpaces $\cV_i$, and the subsets $\cK_i$ are not relevant.
\item Tai \cite{Tai2003} gives values of the constants $C_1$ in \eqref{as:lipschitzrestrictions} for obstacle problem constraint decompositions using $P_1$ FE spaces over a shape-regular and quasi-uniform triangulation.  In particular, constants $C_1$ are know for domain decompositions (with or without an additional coarse mesh) and standard multilevel heirarchies.
% ASSUMING $f$ IS LIPSCHITZ WILL MAKE THE EXISTENCE OF C_2 CLEAR; SEE (14) IN \cite{TaiXu2002}
\end{itemize}

>>>>

\newtheoremstyle{cstyle*}% name
  {5pt}% space above
  {5pt}% space below
  {\itshape}% body font
  {}% indent amount
  {\itshape}% theorem head font
  {.}% punctuation after theorem head
  {.5em}% space after theorem head
  {\thmname{#1}}% theorem head spec
\theoremstyle{cstyle*}
\newtheorem{assumptions*}{Assumptions}

@@

To prove the convergence of the basic algorithm we make two assumptions as follows.

\begin{assumptions*}  \emph{Lipschitz restrictions}: There exists a constant $C_1>0$ so that
\begin{equation}
\left(\sum_{i=0}^{m-1} \|R_i u - R_i v\|^2\right)^{1/2} \le C_1 \|u-v\| \label{as:lipschitzrestrictions}
\end{equation}
for all $u,v\in\cK$.  \emph{Totally Lipschitz residual}: There exists $C_2>0$ so that
\begin{equation}
\sum_{i=0}^{m-1} \sum_{j=0}^{m-1} \left|\ip{f(w_{ij} + v_i) - f(w_{ij})}{y_i}\right| \le C_2 \left(\sum_{i=0}^{m-1} \|v_i\|^2\right)^{1/2} \left(\sum_{i=0}^{m-1} \|y_i\|^2\right)^{1/2} \label{as:totallylipschitzresidual}
\end{equation}
for all $w_{ij} \in \cK$ and $v_i,y_i \in \cV_i$ such that $w_{ij} + v_i \in \cK$ (for all $i,j$).  Note that the constants $C_1,C_2$ generally depend on $m$.
\end{assumptions*}
% IF PROOF BELOW SUCCEEDS, SO ALGORITHM IS NORM DECREASING, THEN MAY BE ABLE TO ARGUE THAT IT IS O.K. FOR CONSTANTS TO DEPEND ON $u,v,w_{ij}$ etc. AS LONG AS THEY ARE UNIFORMLY BOUNDED ON CERTAIN BOUNDED SETS

Though the assumptions are technical in certain senses, the reader should note some essential features:
\begin{itemize}
\item Assumption \eqref{as:lipschitzrestrictions} addresses only the constraint decomposition.  Furthermore, it is often the case that \eqref{as:totallylipschitzresidual} addresses only a subspace decomposition property of the residual functional.  (For example, in the classical obstacle problem \eqref{as:totallylipschitzresidual} is verified over the (sub)spaces $\cV$ and $\cV_i$, and the subsets $\cK$ and $\cK_i$ are not involved.)
\item The assumptions are identical to inequalities (7), (8) in \cite{Tai2003} where they are used to prove convergence of the optimization version(s) of the basic CD algorithm.  See also their unconstrained versions, inequalities (13), (14) in \cite{TaiXu2002}.
\item Tai \cite{Tai2003} gives values of the constants $C_1$ in \eqref{as:lipschitzrestrictions} for obstacle problem constraint decompositions using $P_1$ FE spaces over a shape-regular and quasi-uniform triangulation.  In particular, constants $C_1$ are know for overlapping domain decompositions (with or without an additional coarse mesh) and standard multilevel heirarchies.
% ASSUMING $f$ IS LIPSCHITZ WILL MAKE THE EXISTENCE OF C_2 CLEAR; SEE (14) IN \cite{TaiXu2002}
\end{itemize}
